Text as Policy: Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2016-02-03 manuscript/text_reuse.tex
matching ncsl bills to db
added policy definition start

@@

Condition a) is necessary, since some of the urls returned by the web query refer to blog entries or to protected websites that require NCSL membership. The rationale behind condition b) is to maximize the number of bills we can match to our database (see Figure \ref{fig:bill_desc}). We additionally constrain the number of bills per table to be below 100, in order to assure, that the topic of the table is not too broad. We chose 100 since this number would correspond roughly to two bills per state (often there is a house and a senate bill in each state for a particular policy).
The web query from step 1 returned 266 urls. From the 50 sampled urls 22 fulfilled the three criteria. From these 23 tables we constructed a dataset of [???] bills, of wich we could match [???] to our data base of bill text.

>>>>

\section{Considering  Policy Similarity}

Before

Active within a domain, but possibly moving the status quo in opposite directions. (Glick)
Moving the status quo in a uniform direction, but with different specific policies. (berry berry)
Qualitative classification of the properties of bills adopted within a policy domain (Volden 2006)
Quantitative coding of an important dimension of legislation (e.g., abortion bill restrictiveness) (Mooney and Lee 1992)

In past research on policy adoption, studies have varied in terms of the degrees of similarity between policies

@@

Condition a) is necessary, since some of the urls returned by the web query refer to blog entries or to protected websites that require NCSL membership. The rationale behind condition b) is to maximize the number of bills we can match to our database (see Figure \ref{fig:bill_desc}). We additionally constrain the number of bills per table to be below 100, in order to assure, that the topic of the table is not too broad. We chose 100 since this number would correspond roughly to two bills per state (often there is a house and a senate bill in each state for a particular policy).
The web query from step 1 returned 266 urls. From the 50 sampled urls 22 fulfilled the three criteria. From these 23 tables we constructed a dataset of 950 bills, of which we could match 581 to our bill database.
